Evolutionary market ecologies and market malfunction\\ Draft

### 2021-07-05 draft.tex

\begin{abstract}
    \boldred{Abstract TBA}
\end{abstract}

\section{Introduction}
\boldred{Introduction TBA}
\boldred{Everything related to GP and multi asset: in footnotes}
% Maybe paragraphs could be
% market ecology
% evolutionary computation
% evolution in financial markets

@@

Where $g$ is the dividend growth rate, $\sigma$ its variance, $\omega$ is the autocorrelation parameter of the process, and $Z$ is a standard Wiener process. Based on estimates from Lebaron \cite{lebaron2001empirical} and Scholl et al. \cite{scholl2020market}, we take $g=2\%$ annually and $\sigma = 6\%$ annually. \par
The market is initialised with an initial price of $100$ that matches the fundamental value of the asset, and initial dividends of $100$. 
\boldred{Add a note for the multi asset thing. We actually need to think about multiple assets now that we are doing these big changes. Notably, the ED and TS matrix would change to be $n\timesK$ matrices, where n pop size and K number of assets. The agent strategies change as well to be a K-vector of strategies. It would be better to have a very general case, a very general structure, and so that we have the right structure and only need particular settings or specific small fixes to make it work and extend it.}

>>>>

\begin{abstract}
    In financial markets, distributions of strategies influence market malfunction: misspricing, volatility and inefficiency. Modelling the economy as an ecology of strategies gives insights into market behavior, returns and long term evolution.
    Economic agents are continuously readjusting to the dynamics their interactions create, exploring a large space of possible actions.
    How does this adaptation of trading strategies influence the dynamics of markets and strategies? Does learning improve or undermine a market path to efficiency and equilibrium?
    Here, we study financial adaptation as the evolution of trading strategies using evolutionary algorithms methods in an artificial stock market, and its impact on market and ecology outcomes. 
    \footnote{\textcolor{gray}{Insert summary of main results, contribution of main results to previous knowledge, and more general context of results}}
\end{abstract}

\section{Introduction}

\subsection{Market ecology and malfunction/dynamcs}
\subsection{Learning in financial markets}
\subsection{Research questions and motivation}
\subsection{Model}
\subsection{Main results and implications}

\boldred{Introduction TBD}
\boldred{Everything related to GP and multi asset: in footnotes}
% Maybe paragraphs could be
% market ecology
% evolutionary computation
% evolution in financial markets

@@

Where $g$ is the dividend growth rate, $\sigma$ its variance, $\omega$ is the autocorrelation parameter of the process, and $Z$ is a standard Wiener process. Based on estimates from Lebaron \cite{lebaron2001empirical} and Scholl et al. \cite{scholl2020market}, we take $g=2\%$ annually and $\sigma = 6\%$ annually. \par
The market is initialised with an initial price of $100$ that matches the fundamental value of the asset, and initial dividends of $100$. 
\boldred{Add a note for the multi asset thing. We actually need to think about multiple assets now that we are doing these big changes. Notably, the ED and TS matrix would change to be $nx$ matrices, where n pop size and K number of assets. The agent strategies change as well to be a K-vector of strategies. It would be better to have a very general case, a very general structure, and so that we have the right structure and only need particular settings or specific small fixes to make it work and extend it.}
